---
output:
  pdf_document:
    pandoc_args: --listings
    fig_caption: yes
    includes:
      in_header: "preamble2.tex"
  html_document:
    highlight: kate
    theme: cosmo
    df_print: paged
  word_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r libaries, include=FALSE}
# Import the Library 
library(tidyverse)
library(lubridate)
library(cowplot)
library(kableExtra)
library(readxl)
library(janitor)
library(PropCIs)
library(xtable)
library(esquisse)
library(rio)
library(stringr)
library(zoo)
library(genpwr)
library(stp)
library(broom)
library(haven)
library(anytime)
library(RColorBrewer)

source('color_palettes.R')

script_name <- "Vaccination Weekly Report"
script_run_time <- with_tz(now(), tzone = Sys.getenv("TIME_ZONE"))
Sys.getenv("INSTANCE")

start_date <- as_date("2020-12-16")

end_date <- as_date(Sys.Date())
options(scipen=999)
```

\begin{minipage}{.5\textwidth}\centering
\begin{center}
\includegraphics[width=\textwidth]{UF-College-of-Pharmacy-logo.png}
\end{center}
\end{minipage} \hfill
\begin{minipage}{.5\textwidth}\centering
   

    ONJ Analysis
    
    by Roy Williams MPH

    As of `r end_date`
\end{minipage}


\textcolor[HTML]{`r substring(primary[2], 2)`}{\hrulefill}

```{r}
# Get Frequency Table 
freq<- function(data, colName) {
  
  result <- data %>%
    group_by({{ colName }}) %>%
    tally() %>% 
    drop_na() %>% 
    mutate(percent = str_c("(", round(n / sum(n), 2) * 100, "%)")) %>% 
    arrange(desc(n))
  
  return(result)
}

# Get Proper Kable
tab <- function (.data, ...)
{
  kable_input <-
    knitr::kable(
      .data,
      digits = 3,
      format.args = list(big.mark = ",", scientific = FALSE),
      booktabs = TRUE,
      longtable = TRUE,
      align = "l",
      ...
    ) %>% column_spec(1, width = "10em")
  kable_output <-
    kableExtra::kable_styling(
      kable_input,
      full_width = FALSE,
      position = "center",
      font_size = 10,
      latex_options = c("striped", "repeat_header", "HOLD_position", "scale_down")
    )
  return(kable_output)
}

tab_two <- function (.data, ...)
{
  kable_input <-
    knitr::kable(
      .data,
      digits = 2,
      format.args = list(big.mark = ",", scientific = FALSE),
      booktabs = TRUE,
      longtable = TRUE,
      align = "l",
      ...
    ) %>% column_spec(1, width = "10em")
  kable_output <-
    kableExtra::kable_styling(
      kable_input,
      full_width = FALSE,
      position = "center",
      font_size = 10,
      latex_options = c("striped", "repeat_header", "HOLD_position", "scale_down")
    )
  return(kable_output)
}


# Get Title
title <- function(data) {
  result <- data %>%
    rename_all( ~ gsub("_", " ", .)) %>%
    rename_all(str_to_title)
  
  return(result)
}

bar<-function(data, x, y) {
  ggplot(data, aes(x = reorder({{x}}, -{{y}}), y = {{y}}, fill = {{x}})) + geom_bar(stat = "identity") +geom_text(aes(label = n), vjust = -0.3, size = 3.5)+ theme_minimal() + theme(legend.position="none", panel.grid.major = element_blank()) + theme(plot.title = element_text(hjust=0.5))+scale_fill_brewer(palette="Set3")+ theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) + scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+theme(plot.title = element_text(face="bold"))+theme(axis.title.y = element_text(face="bold")) +
theme(axis.title.x = element_text(face="bold"))
  
}

nb.cols <- 75
mycolors <- colorRampPalette(brewer.pal(75, "Set2"))(nb.cols)


long_bar<-function(data, x, y) {
   ggplot(data, aes(x = reorder({{x}}, {{y}}), y = {{y}}, fill = {{x}})) +
geom_bar(stat = "identity") +
 geom_text(
    aes(label = {{y}}), 
    ## make labels left-aligned
    hjust = 0, size = 2.6, position = position_dodge(0.5)
  ) +
theme_minimal() + 
theme(legend.position="none", panel.grid.major = element_blank()) +
scale_fill_manual(values = mycolors)+
theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
coord_flip()+ theme(legend.position="none", panel.grid.major = element_blank()) + theme(plot.title = element_text(hjust=0.5))+theme(plot.title = element_text(face="bold")) +
theme(axis.title.y = element_text(face="bold")) +
theme(axis.title.x = element_text(face="bold"))


  
}



#Stacked Bar
stacked_bar<-function(data) {
    ggplot(data) +
    geom_bar(aes(x = reorder(var1 , `Value`), y = `Value`, fill = `Col`), stat = "identity") +
    theme_minimal() + scale_fill_brewer(palette = "Pastel2") +
    coord_flip()+
theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+theme(axis.text.y = element_text( size=6.5)) + theme(plot.title = element_text(hjust=0.5))+theme(plot.title = element_text(face="bold")) +
theme(axis.title.y = element_text(face="bold")) +
theme(axis.title.x = element_text(face="bold"))
  
}

kable_it<- function(data) {
  result <- data %>%
  adorn_totals() %>% 
  title() %>% 
  drop_na() %>% 
  tab(caption = "Respondents by Employee_type")
  
  return(result)
}


freq_table<- function(data) {
  result <- data %>%
  lapply(table) %>%
  lapply(as.data.frame) %>%
  Map(bind_cols, var = names(data), .) %>%
  bind_rows() %>%
  select(Var1, Freq) %>%
  arrange(desc(`Freq`)) %>% 
  clean_names()
  
  return(result)
}

pivot_all<-function(data) {
  result <- data %>% 
  pivot_longer(cols = -var1, names_to = "Col", values_to = "Value")
    return(result)
}

# Age Stas
current_age_ds<- function(data, colName) {
  
  result <- data %>%
    group_by({{ colName }}) %>%
    summarize(current_age = mean(current_age),
            median_age = median(current_age),
            n=n(),
            sd=sd(current_age),
            se=sd/sqrt(n)
            ) %>% 
  arrange(desc(n)) %>% 
  title()
  
  return(result)
}


age_ds_overall<- function(data, colName) {
  
  result <- data %>%
    summarize(average_age = mean(age),
            median_age = median(age),
            n=n(),
            sd=sd(age),
            se=sd/sqrt(n)
            ) %>% 
  arrange(desc(n)) %>% 
  title()
  
  return(result)
}

duration_ds<- function(data, colName) {
  
  result <- data %>%
    group_by({{ colName }}) %>%
    summarize(average_duration = mean(duration_lab_to_procedure),
            median_age = median(duration_lab_to_procedure),
            n=n(),
            sd=sd(duration_lab_to_procedure),
            se=sd/sqrt(n)
            ) %>% 
  arrange(desc(n)) %>% 
  title()
  
  return(result)
}


duration_ld <- function(data, colName) {
	result <- data %>%
		group_by({
			{
				colName
			}
		}) %>%
		summarize(
			average_duration = mean(duration_lab_to_diagnosis),
			median_age = median(duration_lab_to_diagnosis),
			n = n(),
			sd = sd(duration_lab_to_diagnosis),
			se = sd / sqrt(n)
		) %>%
		arrange(desc(n)) %>%
		title()
	
	return(result)
}



```

# ONJ Analysis

```{r import data}
# Load DX File
# old <-
#   read_excel(
#     "onj_dx.xlsx",
#     sheet = 1,
#     col_names = TRUE,
#     col_types = NULL,
#     na = "",
#     skip = 0
#   ) %>% select(-"...1") %>% clean_names()

#Load Cancer Patients Only
dx <-
  read_excel(
    "/Users/roy/downloads/onj_dx_cancer_only_demographics.xlsx",
    sheet = 1,
    col_names = TRUE,
    col_types = NULL,
    na = "",
    skip = 0
  ) %>% select(-"...1") %>% clean_names()

meds <-
  read_excel(
    "/Users/roy/downloads/onj_meds_demos_0422.xlsx",
    sheet = 1,
    col_names = TRUE,
    col_types = NULL,
    na = "",
    skip = 0
  ) %>% select(-"...1") %>%
  clean_names() %>% 
	group_by(id)#
	#filter(rx_start_date == min(rx_start_date))

meds_mtor <-
  read_excel(
    "/Users/roy/downloads/onj_meds_mtor.xlsx",
    sheet = 1,
    col_names = TRUE,
    col_types = NULL,
    na = "",
    skip = 0
  ) %>% select(-"...1") %>%
  clean_names() %>% 
	group_by(id) #%>% 
#	filter(rx_start_date == min(rx_start_date))

meds_total<-inner_join(meds, meds_mtor, by = "id")





distinct_dx<-dx %>% 
   distinct(id, dx, .keep_all= TRUE)

# distinct_dx_old <-old %>%
#    distinct(id, raw_dx, .keep_all= TRUE)


distinct_freq<-distinct_dx %>% 
  freq(dx) %>% 
  adorn_totals() %>% 
  tab(caption = "Number of Unique Individuals with a ONJ Diagnosis Code in One FL Data")
distinct_freq

distinct_meds<-meds %>% 
  distinct(id, raw_rx_med_name, .keep_all= TRUE) %>% 
  mutate(raw_rx_med_name = sub(" .*", "", raw_rx_med_name))



distinct_meds_freq<-distinct_meds %>%
  mutate(raw_rx_med_name = tolower(raw_rx_med_name)) %>% 
  freq(raw_rx_med_name) %>%
  adorn_totals() %>% 
  tab(caption = "Number of Unique Individuals on Bisphosonate Prescriptions or RANKL Inhibitors in One FL Data excluding patients with an Antiangiogenic Agent and or m-TOR Inhibitor prescription.") 
distinct_meds_freq

# Both Drugs and Diagnosis 


distinct_both <- distinct_meds %>%
  inner_join(distinct_dx, by = "id") %>%
  group_by(raw_rx_med_name) %>%
  mutate(raw_rx_med_name = tolower(raw_rx_med_name)) %>%
  mutate(raw_rx_med_name = recode(raw_rx_med_name,
                                  `boniva` = "ibandronate",
                                  `fosamax` = "alendronate",
                                  `prolia` = "denosumab",
                                  `xgeva` = "denosumab",
                                  `zometa` = "zoledronate",
                                  `zoledronic` = "zoledronate",
                                  `zoldronic` = "zoledronate",
                                  `inv`= "denosumab" )) %>%
 tally() %>%
  adorn_totals() %>%
  tab(caption = "Number of Unique Inviduals on Bisphosonate Prescriptions or RANKL Inhibitors and ONJ diagnosis excluding patients with an Antiangiogenic Agent and or m-TOR Inhibitor prescription")
 distinct_both

# distinct_both_classes<-distinct_both %>% 
#   mutate(iv_bp = case_when(raw_rx_med_name == 'zoledronate' ~ "zoledronate",
#                          'ibandronate' ~ "ibandronate"  )) #%>% 
#   mutate(iv_bp = case_when(raw_rx_med_name == 'ibandronate' ~ "ibandronate"))
 
 
   # mutate(iv = case_when(is.na(lymph_dx) ~ 0,
   #                         TRUE ~ 1))

 # mutate(race = case_when(hispanic== 'Hispanic' ~ "Hispanic",
 #                          TRUE ~ race))

```

# Summary 
Overall, there were **78,742** prescriptions of either Bisphosonate or RANKL Inhibitors found in One Florida data. Of these prescriptions, **15,124** correspond to unique patients.

In addition, **409** patients were found that had an ICD code corresponding to ONJ and did not have an ICD code corresponding to Osteoporosis (M80* - M90*, or 733.0* ) Of these patients, **44** had a prescription record containing either Bisphosonate and or RANKL Inhibitors and were not prescribed an Antiangiogenic Agent and or m-TOR Inhibitor.